Estimating Access to Rabies Post-Exposure Prophylaxis in Madagascar

### 2019-02-27 accessPEP.Rmd
all the messy model fitting code

ctar %>%
  left_join(select(mada_communes@data, commune, mdg_cm_, mtch_ds), 
            by = c("commune" = "commune", "district" = "mtch_ds")) %>%
  filter(consult.type == "Animal bite/exposure") %>%
  group_by(mdg_cm_) %>%
  summarize(bites = round(n()/n_months*12)) %>%
  left_join(comm_data) %>%
  filter(!is.na(ttimes_weighted), 
         district %in% mada_district@data$district[mada_district@data$CTAR == "Moramanga"]) -> mora_bites
```

@@

ctar_check %>% 
  filter(exclude_bydate == 0, exclude_bycomment == 0) %>% # exclude contacts
  mutate_at(vars(starts_with("date")), funs(ymd(.))) %>% # format dates
  group_by(year = year(date_de_consultation), district, id_ctar) %>% # group by year and district
  summarize(n = n()) %>% # get count of exposures
  left_join(covars) %>% # add pop + ttimes + reporting
  left_join(clinic_reporting) %>%   # add reporting by clinic + year
  filter(exclude == 0, prop > 0.25) %>% ## filter out excluded catchments and ones with < 25% reporting
  group_by(district, year) %>%
  mutate(bites = n/prop) %>%
  summarise(bites = sum(bites, na.rm = TRUE)) %>%
  left_join(covars) -> exps

@@

To estimate the average number of deaths for each commune, we extended the above framework into a stochastic framework as follows (TO DO: take neg bin around min and max for RI instead):
$$
deaths_i = (R_i - p_{rabid}B_i) \times p_{death}
$$
where $R_i$ is drawn from a uniform distribution between the minimum and maximum expected number of human exposures for each location and $B_i$, the number of reported bites, is drawn from a poisson distribution with the mean predicted number of bites from the travel time model. We constrain $p_rabid$ as in Equation N, and we assume that all rabies exposures reported to an ARMC receive and complete PEP, and PEP is completely effective at preventing death due to rabies. The probability of death in the absence of PEP is taken from cite GAVI/Joel paper.  
<br>

### Strategically expanding PEP access
Given limited resources and capacity of clinics to provision PEP, we developed a framework to look at the incremental benefit of expanding PEP provisioning to additional ARMC. Starting with the current locations, we added one clinic and recalculated the proportion of people living < 3 hours away from a clinic for the country. We added the clinic which minimized this metric, and then repeated the process iteratively, ranking clinics and adding the top clinic sequentially. We calculate burden for the given clinic locations and look at the incremental reduction in burden as each clinic is added.

### Sensitivity analyses for burden estimates 
- R (increasing or decreasing with pop) (min + max)
- P-rabid min and max
- Probability of death min and max
- Look at change in raw # of deaths and also change in burden by scenarios

@@

### Models of bites as a function of travel times
```{r likelihood of observing moramanga data @ commune level, fig.cap = "Figure 5A"}
library(boot)

get.likelihood.bites <- function(bites, covar, pop, params) {
  beta <- params[1]
  intercept <- params[2]
  exp_bites <- inv.logit(beta*covar + intercept)*pop
  return(-sum(dpois(round(bites), lambda = exp_bites, log = TRUE)))
}

get.likelihood.mora <- function(commune, params) {
  # To test likelihood function
  # commune = comm_data
  # district = exps_dist
  # params = c(1e-6, 0.1)
  B_ttimes <- params[1]
  B_0 <- params[2]
  commune %>%
      mutate(bites_mu = inv.logit(B_ttimes*ttimes_weighted + B_0)*pop) -> sum_bites
  return(-sum(dpois(round(sum_bites$), lambda = sum_bites$bites_mu, log = TRUE)))
}

get.likelihood.mada <- function(commune, district, params) {
  # To test likelihood function
  # commune = comm_data
  # district = exps_dist
  # params = c(1e-6, 0.1)
  B_ttimes <- params[1]
  B_0 <- params[2]
  commune %>%
      filter(exclude == 0) %>%
      group_by(mdg_dis_co) %>%
      mutate(bites = inv.logit(B_ttimes*ttimes_weighted + B_0)*pop) %>%
      summarize(sum_bites = sum(bites)) %>%
      left_join(select(district, district, dist_bites = bites), 
                by = c("mdg_dis_co" = "district")) %>%
      filter(!is.na(dist_bites)) -> sum_bites
  return(-sum(dpois(round(sum_bites$dist_bites), lambda = sum_bites$sum_bites, log = TRUE)))
}
get.likelihood.dist <- function(district, params) {
  # To test likelihood function
  # commune = comm_data
  # district = exps_dist
  # params = c(1e-6, 0.1)
  B_ttimes <- params[1]
  B_0 <- params[2]
  district %>%
      filter(exclude == 0) %>%
      mutate(exp_bites = inv.logit(B_ttimes*ttimes_weighted_dist + B_0)*pop) -> district
  return(-sum(dpois(round(district$exp_bites), lambda = round(district$bites), log = TRUE)))
}

### Moramanga model ###
mora_pars <- optim(par = c(1e-6, 0.1), get.likelihood.mora, commune = mora_bites, hessian = TRUE)
B_ttimes_mora <- mora_pars$par[1]
B_0_mora <- mora_pars$par[2]

## Getting standard errors
# this is how you can get standard errors from optim, but inverting the hessian
se <- sqrt(abs(diag(solve(mora_pars$hessian)))); se

#simulate "standard errors"
varcov <- solve(mora_pars$hessian)

ntest = 1000; testpar = mora_pars$par; sim.par = matrix(NA, ntest, 2)
for (k in 1:ntest) {
  sim.par[k, ] = mvrnorm(1, mora_pars$par, varcov)
}

B_ttimes_mora_CI <- quantile(sim.par[,1],c(0.025,0.975))
B_0_mora_CI <- quantile(sim.par[,2],c(0.025,0.975))

### Madagascar model ###
mada_pars <- optim(par = c(1e-6, 0.1), get.likelihood.mada, district = exps_dist,
             commune = comm_data, hessian = TRUE)
B_ttimes_mada <- mada_pars$par[1]
B_0_mada <- mada_pars$par[2]

## Getting standard errors
# this is how you can get standard errors from optim, but inverting the hessian
se <- sqrt(abs(diag(solve(mada_pars$hessian)))); se

#simulate "standard errors"
varcov <- solve(mada_pars$hessian)

ntest = 1000; testpar = mada_pars$par; sim.par = matrix(NA, ntest, 2)
for (k in 1:ntest) {
  sim.par[k, ] = mvrnorm(1, mada_pars$par, varcov)
}

B_ttimes_mada_CI <- quantile(sim.par[,1],c(0.025,0.975))
B_0_mada_CI <- quantile(sim.par[,2],c(0.025,0.975))

### District parameters
dist_pars <- optim(par = c(1e-6, 0.1), get.likelihood.dist, district = exps_dist,
              hessian = TRUE)
B_ttimes_dist <- dist_pars$par[1]
B_0_dist <- dist_pars$par[2]

@@

preds <- foreach(i = 1:nrow(par_df), .combine = rbind) %do% {
  bites <- inv.logit(par_df$B_ttimes[i]*ttimes_plot + par_df$B_0[i])*pop_plot
  upper <- inv.logit(par_df$B_ttimes_upper[i]*ttimes_plot + par_df$B_0_upper[i])*pop_plot
  lower <- inv.logit(par_df$B_ttimes_lower[i]*ttimes_plot + par_df$B_0_lower[i])*pop_plot
  return(as.data.frame(list(bites = bites, upper = upper, lower = lower, ttimes = ttimes_plot/60, 
                            model = par_df$model[i])))
}
ggplot(data = preds, aes(x = ttimes, y = bites, color = model)) +
  geom_line() +
  geom_ribbon(aes(ymin = lower, ymax = upper, fill = model), alpha = 0.5) +

plot(ttimes_plot/60, inv.logit(B_ttimes_mada*ttimes_plot + B_0_mada)*pop_plot, type = "l", bty = "l",
     ylab = "Mean bites per 100k", xlab = "Travel times (hrs)", col = "darkblue")
points(ttimes_plot/60, inv.logit(B_ttimes_mada_CI[1]*ttimes_plot + B_0_mada_CI[1])*pop_plot, type = "l", 
       lty = 2, col = "lightblue")
points(ttimes_plot/60, inv.logit(B_ttimes_mada_CI[2]*ttimes_plot + B_0_mada_CI[2])*pop_plot, type = "l", 
       lty = 2, col = "lightblue")

points(ttimes_plot/60, inv.logit(B_ttimes_mora*ttimes_plot + B_0_mora)*pop_plot, type = "l", col = "red")
points(ttimes_plot/60, inv.logit(B_ttimes_mora_CI[1]*ttimes_plot + B_0_mora_CI[1])*pop_plot, type = "l", 
       lty = 2, col = "pink")
points(ttimes_plot/60, inv.logit(B_ttimes_mora_CI[2]*ttimes_plot + B_0_mora_CI[2])*pop_plot, type = "l",
       lty = 2, col = "pink")

points(ttimes_plot/60, inv.logit(B_ttimes_dist*ttimes_plot + B_0_dist)*pop_plot, type = "l", col = "purple")
points(ttimes_plot/60, inv(B_ttimes_dist_CI[1]*ttimes_plot + B_0_dist_CI[1])*pop_plot, type = "l", 
       lty = 2, col = "lavender")
points(ttimes_plot/60, exp(B_ttimes_dist_CI[2]*ttimes_plot + B_0_dist_CI[2])*pop_plot, type = "l",
       lty = 2, col = "lavender")

legend("topright", c("Mada communes", "Mada districts", "Moramanga communes"), 
       col = c("darkblue", "purple", "red"), 
       lty = c(1, 1, 1), 
       bty = "n")
```

>>>>

ctar %>%
  left_join(select(mada_communes@data, commune, mdg_cm_, mtch_ds), 
            by = c("commune" = "commune", "district" = "mtch_ds")) %>%
  filter(consult.type == "Animal bite/exposure") %>%
  group_by(mdg_cm_) %>%
  summarize(bites = round(n()/n_months*12)) %>%
  right_join(filter(comm_data, CTAR == "Moramanga")) %>% ## only districts within catchment (@ comm level)
  filter(!is.na(ttimes_weighted), 
         dist_catch == "Moramanga") %>%
  replace_na(list(bites = 0)) -> mora_bites
```

@@

ctar_check %>% 
  filter(exclude_bydate == 0, exclude_bycomment == 0) %>% # exclude contacts
  mutate_at(vars(starts_with("date")), funs(ymd(.))) %>% # format dates
  group_by(year = year(date_de_consultation), district, id_ctar) %>% # group by year and district
  summarize(n = n()) %>% # get count of exposures
  left_join(covars) %>% # add pop + ttimes + reporting
  left_join(clinic_reporting) %>%   # add reporting by clinic + year
  filter(exclude == 0, prop > 0.25) %>% ## filter out excluded catchments and ones with < 25% reporting
  group_by(district, year) %>%
  mutate(bites = n/prop) %>%
  summarise(bites = sum(bites, na.rm = TRUE)) %>%
  right_join(covars) %>%
  filter(exclude == 0) %>%
  replace_na(list(bites = 0)) -> exps

@@

To estimate the average number of deaths for each commune, we extended the above framework into a stochastic framework as follows):
$$
deaths_i = (R_i - p_{rabid_i}B_i) \times p_{death}
$$
where $R_i$ is drawn from a uniform distribution between the minimum and maximum expected number of human exposures for each location and $B_i$, the number of reported bites, is drawn from a poisson distribution with the mean predicted number of bites from the travel time model. We draw $p_rabid_i$ from a uniform distribution between 0.2 - 0.6, while constraining it as per Equation N. We assume that all rabies exposed patients who report to an ARMC receive and complete PEP, and PEP is completely effective at preventing death due to rabies. The probability of death in the absence of PEP is taken from cite GAVI/Joel paper.  
<br>

### Strategically expanding PEP access
Given limited resources and capacity of clinics to provision PEP, we developed a framework to look at the incremental benefit of expanding PEP provisioning to additional ARMC. Starting with the current locations, we added one clinic at a time, calculating the proportion of people living < 3 hours away from any clinic for the country. We added the clinic which minimized this metric, and then repeated the process iteratively, ranking clinics and adding the top clinic sequentially. We calculate burden for the given clinic locations and look at the incremental reduction in burden as each clinic is added.

### Sensitivity analyses for burden estimates 
We estimate burden deterministically across a range of parameter values to test the effects of our model assumptions on estimates of rabies burden. Specifically, we fix rabies incidence at the minimum and maximum of our estimated range, look at the range of values of p_rabid between 0.2 - 0.6 (as per Moramanga), and the range of values of rho_max (0.85 - 0.99) to get at maximum and minimum estimates of burden. We also examine the impact of systematic variation in rabies incidence with human population (a potential proxy for changes in the dog population/HDR) by looking at how estimates of burden changes if rabies incidence were to scale positively or negatively with human population.

@@

### Models of bites as a function of travel times
```{r likelihood of observing moramanga data @ commune level, fig.cap = "Figure 5A"}
library(boot)
likelihoods <- list(
  get.likelihood.bites = function(bites, covar, pop, beta, intercept, ...) {
    exp_bites <- inv.logit(beta*covar + intercept)*pop
    return(-sum(dpois(round(bites), lambda = exp_bites, log = TRUE)))
  },
  get.likelihood.sumbites = function(bites, aggregate_bites, covar_agg, aggregate_covar, 
                                     pop_agg, beta, 
                                     intercept, ...) {
    exp_bites <- inv.logit(beta*covar_agg + intercept)*pop_agg
    df <- as.data.frame(list(exp_bites = exp_bites, names = aggregate_covar))
    df %>%
      group_by(names) %>%
      summarize(sum_bites = sum(exp_bites, na.rm = TRUE)) %>%
      left_join(as.data.frame(list(bites = bites, names = aggregate_bites))) -> sum_bites
    return(-sum(dpois(round(sum_bites$bites), lambda = sum_bites$sum_bites, log = TRUE)))
  }, 
  get.likelihood.pop = function(bites, pop, beta, intercept, trans...) {
    exp_bites <- exp(beta*pop/trans + intercept)
    return(-sum(dpois(round(bites), lambda = exp_bites, log = TRUE)))
  },
  get.likelihood.sumpop = function(bites, aggregate_bites, aggregate_covar, pop_agg, beta, 
                                   intercept, trans, ...) {
    exp_bites <- exp(beta*pop_agg/trans + intercept)
    df <- as.data.frame(list(exp_bites = exp_bites, names = aggregate_covar))
    df %>%
      group_by(names) %>%
      summarize(sum_bites = sum(exp_bites, na.rm = TRUE)) %>%
      left_join(as.data.frame(list(bites = bites, names = aggregate_bites))) -> sum_bites
    return(-sum(dpois(round(sum_bites$bites), lambda = sum_bites$sum_bites, log = TRUE)))
  })

mods_mada <- lapply(likelihoods, function(x) mle2(minuslogl = x, 
                                     data = list(bites = exps_dist$bites, 
                                                 aggregate_bites = exps_dist$district,
                                                 aggregate_covar = comm_data$mdg_dis_co,
                                                 covar_agg = comm_data$ttimes_weighted/60,
                                                 covar = exps_dist$ttimes_weighted_dist/60, 
                                                 pop = exps_dist$pop, 
                                                 pop_agg = comm_data$pop, trans = 1e5), 
       start = list(beta = 1e-5, intercept = 0.1)))
prof_CI <- lapply(mods_mada, confint)

mada_mod_predicts <- as.data.frame(list(beta = mapply(function(x) coef(x)["beta"], mods_mada), 
     intercept = mapply(function(x) coef(x)["intercept"], mods_mada), 
     beta_upper = mapply(function(x) x["beta", 2], prof_CI),
     beta_lower = mapply(function(x) x["beta", 1], prof_CI),
     intercept_upper = mapply(function(x) x["intercept", 2], prof_CI),
     intercept_lower = mapply(function(x) x["intercept", 1], prof_CI),
     likelihood = mapply(function(x) logLik(x), mods_mada),
     data = "Mada"))

mada_mod_results <- as.data.frame(list(params = c("beta", "intercept"), 
                   estimates = t(mapply(function(x) coef(x), mods_mada)), 
                   upper = t(mapply(function(x) x[, 2], prof_CI)),
                   lower = t(mapply(function(x) x[, 1], prof_CI)), 
                   data = "Mada"))

## Predictions
library(foreach)
predicts <- list(
  pred.ttimes = function(bites, covar, pop, beta, intercept, ...) {
    exp_bites <- inv.logit(beta*covar + intercept)*pop
    return(as.data.frame(list(observed = bites, 
                              predicted = rpois(length(bites), exp_bites))))
  },
  pred.sumttimes = function(bites, aggregate_bites, covar_agg, aggregate_covar, 
                                     pop_agg, beta, 
                                     intercept, ...) {
    exp_bites <- inv.logit(beta*covar_agg + intercept)*pop_agg
    df <- as.data.frame(list(exp_bites = exp_bites, names = aggregate_covar))
    df %>%
      group_by(names) %>%
      summarize(sum_bites = sum(exp_bites, na.rm = TRUE)) %>%
      left_join(as.data.frame(list(bites = bites, names = aggregate_bites))) -> sum_bites
    return(as.data.frame(list(observed = sum_bites$bites, 
                              predicted = rpois(nrow(sum_bites), sum_bites$sum_bites))))
  }, 
  pred.pop = function(bites, pop, beta, intercept, trans, ...) {
    exp_bites <- exp(beta*pop/trans + intercept)
   return(as.data.frame(list(observed = bites, 
                              predicted = rpois(length(bites), exp_bites))))
  },
  pred.sumpop = function(bites, aggregate_bites, aggregate_covar, pop_agg, beta, 
                                   intercept, trans, ...) {
    exp_bites <- exp(beta*pop_agg/trans + intercept)
    df <- as.data.frame(list(exp_bites = exp_bites, names = aggregate_covar))
    df %>%
      group_by(names) %>%
      summarize(sum_bites = sum(exp_bites, na.rm = TRUE)) %>%
      left_join(as.data.frame(list(bites = bites, names = aggregate_bites))) -> sum_bites
    return(as.data.frame(list(observed = sum_bites$bites, 
                              predicted = rpois(nrow(sum_bites), sum_bites$sum_bites))))
  })
mada_mod_predicts$predict_fun <- predicts
preds <- foreach(i = 1:nrow(mada_mod_predicts), .combine = rbind) %do% {

  check <- mada_mod_predicts$predict_fun[[i]]

  pred <- check(beta = mada_mod_predicts$beta[i], intercept = mada_mod_predicts$intercept[i],
          bites = exps_dist$bites, aggregate_bites = exps_dist$district,
          aggregate_covar = comm_data$mdg_dis_co, covar_agg = comm_data$ttimes_weighted/60,
          covar = exps_dist$ttimes_weighted_dist/60, 
          pop = exps_dist$pop, pop_agg = comm_data$pop, trans = 1e5)

  pred$upper <- check(beta = mada_mod_predicts$beta_upper[i], 
                      intercept = mada_mod_predicts$intercept_upper[i],
                      bites = exps_dist$bites, aggregate_bites = exps_dist$district,
                      aggregate_covar = comm_data$mdg_dis_co, covar_agg = comm_data$ttimes_weighted/60,
                      covar = exps_dist$ttimes_weighted_dist/60, 
                      pop = exps_dist$pop, pop_agg = comm_data$pop, trans = 1e5)$predicted
  pred$lower <- check(beta = mada_mod_predicts$beta_lower[i], 
                      intercept = mada_mod_predicts$intercept_lower[i],
                      bites = exps_dist$bites, aggregate_bites = exps_dist$district,
                      covar = exps_dist$ttimes_weighted_dist/60, 
                      aggregate_covar = comm_data$mdg_dis_co, covar_agg = comm_data$ttimes_weighted/60,
                      pop = exps_dist$pop, pop_agg = comm_data$pop, trans = 1e5)$predicted

  pred$model <- rownames(mada_mod_predicts)[i]
  pred$data <- mada_mod_predicts$data[i]
  pred
}

expected <- list(
  pred.ttimes = function(covar, pop, beta, intercept, ...) {
    return(inv.logit(beta*covar + intercept)*pop)
  },
  pred.sumttimes = function(covar, pop, beta, 
                                     intercept, ...) {
    return(inv.logit(beta*covar + intercept)*pop)
  }, 
  pred.pop = function(pop_covar, beta, intercept, trans, ...) {
   return(exp(beta*pop_covar/trans + intercept))
  },
  pred.sumpop = function(pop_covar, beta, intercept, trans, ...) {
    return(exp(beta*pop_covar/trans + intercept))
  })
mada_mod_predicts$expect_fun <- expected
ttimes_plot <- seq(0, 720, by = 30)
pop_plot <- seq(100, 1e6, length.out = length(ttimes_plot))
expect <- foreach(i = 1:nrow(mada_mod_predicts), .combine = rbind) %do% {
  check <- mada_mod_predicts$expect_fun[[i]]
  exp <- check(beta = mada_mod_predicts$beta[i], intercept = mada_mod_predicts$intercept[i],
               covar = ttimes_plot/60, pop = 1e5, pop_covar = pop_plot, 
               trans = 1e5)
  exp_upper <- check(beta = mada_mod_predicts$beta_upper[i], 
                     intercept = mada_mod_predicts$intercept_upper[i],
                     covar = ttimes_plot/60, pop = 1e5, pop_covar = pop_plot, trans = 1e5)
  exp_lower <- check(beta = mada_mod_predicts$beta_lower[i], 
                     intercept = mada_mod_predicts$intercept_lower[i],
                     covar = ttimes_plot/60, pop = 1e5, pop_covar = pop_plot, trans = 1e5)
  as.data.frame(list(ttimes = ttimes_plot, 
                     pop = pop_plot, exp = exp, exp_upper = exp_upper, exp_lower = exp_lower, 
                     model = rownames(mada_mod_predicts)[i], data = mada_mod_predicts$data[i]))
}

ggplot(data = preds, aes(x = observed, y = predicted, color = model)) +
  geom_point() +
  geom_abline(intercept = 0, slope = 1, linetype = 2, color = "grey")
ggplot(data = filter(expect, !grepl("pop", model, fixed = TRUE)), 
       aes(x = ttimes, y = exp, color = model)) +
  geom_line() +
  geom_ribbon(aes(ymin = exp_lower, ymax = exp_upper, fill = model), alpha = 0.5)

## Mada pars
library(bbmle)
mada_ttimes_fit <- mle2(get.likelihood.bites, start = list(beta = 1e-4, intercept = 0.1), 
                  data = list(bites = exps_dist$bites, covar = exps_dist$ttimes_weighted_dist, 
                              pop = exps_dist$pop))
mada_sumttimes_fit <- mle2(get.likelihood.sumbites, start = list(beta = 1e-5, intercept = 0.1), 
                  data = list(bites = exps_dist$bites, aggregate_bites = exps_dist$district,
                              covar = comm_data$ttimes_weighted, 
                              aggregate_covar = comm_data$mdg_dis_co,
                              pop = comm_data$pop))
## Pop
mada_pop_fit <- mle2(get.likelihood.pop, start = list(beta = 1e-5, intercept = 0.1), 
                  data = list(bites = exps_dist$bites, pop = exps_dist$pop/1e5))
mada_sumpop_fit <- mle2(get.likelihood.sumpop, start = list(beta = 1e-5, intercept = 0.1), 
                  data = list(bites = exps_dist$bites, aggregate_bites = exps_dist$district,
                              aggregate_covar = comm_data$mdg_dis_co,
                              pop = comm_data$pop/1e5))

## Distance to CTAR
ctar_coords <- cbind(ctar_metadata$LONGITUDE, ctar_metadata$LATITUDE)
district_coords <- coordinates(mada_district)
library(geosphere)
distance_mat <- distm(district_coords, ctar_coords)
mada_district$dist_min <- apply(distance_mat, 1, min)/1000
exps_dist$dist_min <- mada_district$dist_min[match(exps_dist$district, mada_district$mdg_dis_co)]
mada_distance_fit <- mle2(get.likelihood.bites, start = list(beta = 1e-5, intercept = 0.1), 
                  data = list(bites = exps_dist$bites, covar = exps_dist$dist_min, 
                              pop = exps_dist$pop))

mada_communes@data %>%
  mutate(long = coordinates(mada_communes)[, 1], lat = coordinates(mada_communes)[, 2]) %>%
  select(commune, mdg_cm_, mtch_ds, long, lat) %>%
  right_join(comm_data) %>%
  mutate(distance = apply(distm(select(., long, lat), ctar_coords), 1, min)/1000) -> comm_data
mada_sumdist_fit <- mle2(get.likelihood.sumbites, start = list(beta = 1e-5, intercept = 0.1), 
                  data = list(bites = exps_dist$bites, aggregate_bites = exps_dist$district,
                              covar = comm_data$distance, 
                              aggregate_covar = comm_data$mdg_dis_co,
                              pop = comm_data$pop))

plot(exps_dist$bites, inv.logit(mada_distance_fit@coef["beta"]*exps_dist$dist_min +
                                  mada_distance_fit@coef["intercept"])*exps_dist$pop)
points(exps_dist$bites, inv.logit(mada_ttimes_fit@coef["beta"]*exps_dist$ttimes_weighted_dist +
                                  mada_ttimes_fit@coef["intercept"])*exps_dist$pop, col = "blue")
points(exps_dist$bites, exp(mada_pop_fit@coef["beta"]*exps_dist$pop/1e5 +
                                  mada_pop_fit@coef["intercept"]), col = "red")
abline(a = 0, b = 1, lty = 2)
AICctab(mada_ttimes_fit, mada_distance_fit, mada_pop_fit, mada_sumttimes_fit, mada_sumpop_fit,
        mada_sumdist_fit, nobs = nrow(exps_dist))

### Moramanga model ###
mora_coords <- cbind(ctar_metadata$LONGITUDE[ctar_metadata$CTAR == "Moramanga"], 
                     ctar_metadata$LATITUDE[ctar_metadata$CTAR == "Moramanga"])
library(geosphere)
mada_communes@data %>%
  mutate(long = coordinates(mada_communes)[, 1], lat = coordinates(mada_communes)[, 2]) %>%
  select(commune, mdg_cm_, mtch_ds, long, lat) %>%
  right_join(mora_bites) %>%
  mutate(distance = distm(select(mora_bites, long, lat), mora_coords)[, 1]/1000) -> mora_bites
mora_distance_fit <- mle2(get.likelihood.bites, start = list(beta = 1e-5, intercept = 0.1), 
                  data = list(bites = mora_bites$bites, covar = mora_bites$distance, 
                              pop = mora_bites$pop))
mora_pop_fit <- mle2(get.likelihood.pop, start = list(beta = 1e-5, intercept = 0.1), 
                  data = list(bites = mora_bites$bites, pop = mora_bites$pop/1e5))
mora_ttimes_fit <- mle2(get.likelihood.bites, start = list(beta = 1e-5, intercept = 0.1), 
                  data = list(bites = mora_bites$bites, covar = mora_bites$ttimes_weighted/60, 
                              pop = mora_bites$pop))
AICctab(mora_ttimes_fit, mora_distance_fit, mora_pop_fit, nobs = nrow(mora_bites))

mada_check_fit <- mle2(get.likelihood.bites, start = list(beta = 1e-5, intercept = 0.1), 
                  data = list(bites = exps_dist$bites, covar = exps_dist$pop/1e5, 
                              pop = exps_dist$pop))
mora_check_fit <- mle2(get.likelihood.bites, start = list(beta = 1e-5, intercept = 0.1), 
                  data = list(bites = mora_bites$bites, covar = mora_bites$pop/1e5, 
                              pop = mora_bites$pop))

@@

preds <- foreach(i = 1:nrow(par_df), .combine = rbind) %do% {
  bites <- inv.logit(par_df$B_ttimes[i]*ttimes_plot + par_df$B_0[i])*pop_plot
  upper <- inv.logit(par_df$B_ttimes_upper[i]*ttimes_plot + par_df$B_0_upper[i])*pop_plot
  lower <- inv.logit(par_df$B_ttimes_lower[i]*ttimes_plot + par_df$B_0_lower[i])*pop_plot
  return(as.data.frame(list(bites = bites, upper = upper, lower = lower, ttimes = ttimes_plot/60, 
                            model = par_df$model[i])))
}
ggplot(data = preds, aes(x = ttimes, y = bites, color = model)) +
  geom_line() +
  geom_ribbon(aes(ymin = lower, ymax = upper, fill = model), alpha = 0.5)
```
